\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{float} 
\usepackage{amsfonts}
\parskip 0.1in
\usepackage[margin=1.4in]{geometry}

 \usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
\rhead{G28 Workshop Four}
\lhead{Charles Rahal}
\rfoot{Page \thepage}
 
\begin{document}
\small
\subsubsection*{Econometrics with Financial Applications: Workshop Four}
\textit{In this class we'll estimate a vector error correction model and then write a program with rolling windows to show the stability of the cointegrating rank$\backslash$vector.}
\begin{enumerate}
\item Download three series: \emph{indpro} (ind. prod), \emph{pce} (cons) and \emph{m2real} (M2):
\begin{center}
\texttt{wfcreate m 1970m1 2014m9\\
fetch FRED::\emph{series}}
\end{center}
\item Again plot the three series:
\begin{center}
\texttt{graph plottedseries.line log(indpro) log(pce) log(m2real) \\
plottedseries.seetelem(1) axis(right)}

\end{center}
\item Run a series of ADF tests to determine their stationarity. 
\item Generate three new variables and group them:
\begin{center}
\texttt{group threeserieslogged lindpro lpce lm2real}
\end{center}
\item To run Johansen cointegration tests, click \emph{View}$\rightarrow$\emph{Cointegration Test}$\rightarrow$\emph{Johansen Test} from VAR or Group objects. While $k$ is typically chosen through an IC on a VAR in first differences, try the tests for various lag lengths:
\begin{center}
\texttt{freeze(cointtest\{!k\}) threeserieslogged.coint(s,!k)}
\end{center}
\item Now try the VAR in first differences as before:\\
\begin{center}
\texttt{
var firstdifferences.ls 1 4 d(lindpro) d(lpce) d(lm2real)
firstdifferences.laglen(12)
}

\end{center}
\item Lets now consider how stable this relationship is by estimating the test as a rolling window:
\begin{center}
\texttt{vector(240) ranks\\
for !k = 1 to 240\\
smpl @first+!k @last-240+!k\\
freeze(vecmtable{!k}) threeserieslogged.coint(s,4)\\
ranks(!k) = vecmtable{!k}(13,4)\\
next\\
freeze(cointegratingranks) ranks.line}
\end{center}
Experiment with window size? What can we conclude? What was our hypothesis? Does money affect long run production or consumption?
\item Lets test whether money does not enter into the long run relationship:
\begin{center}
\texttt{
var firstvecm\\
firstvecm.append(coint) b(1,3)=0\\
firstvecm.ec(c,1,restrict) 1 1 lpce lindpro lm2real
}
\end{center}
First a VEC, `firstvecm' is declared, then a restriction is appended to `firstvecm', finally `firstvecm' is estimated with that restriction imposed. Alternatively, this can be imposed on a standard VECM: \emph{Proc}$\rightarrow$\emph{Specify/Estimate}$\rightarrow$\emph{VECM Restrictions}$\rightarrow$\emph{Impose Restrictions(B(1,3)=0).}
\item View the cointegrating graph (\emph{View}$\rightarrow$\emph{Cointegrating Graph}).
\item Consider the program on the following page for how to run all of these commands in a batch environment.
\end{enumerate}
\newpage
\subsubsection*{Program for Workshop Four}
\noindent wfcreate m 1959m1 2014m09\\
fetch fred::indpro\\
fetch fred::m2real\\
fetch fred::pce\\
genr lindpro=log(indpro)\\
genr lpce=log(pce)\\
genr lm2real=log(m2real)\\
graph loggedseries.line lindpro lpce lm2real\\
loggedseries.setelem(1) axis(right)\\
for \%series lindpro lpce lm2real\\
\indent	for \%det const trend\\
\indent \indent		freeze(\{\%series\}\_\{\%det\}\_d0) \{\%series\}.uroot(adf,\{\%det\},dif=0)\\
\indent \indent		freeze(\{\%series\}\_\{\%det\}\_d1) \{\%series\}.uroot(adf,\{\%det\},dif=1)\\
\indent \indent		freeze(\{\%series\}\_\{\%det\}\_d2) \{\%series\}.uroot(adf,\{\%det\},dif=2)\\
\indent	next\\
\indent	freeze(\{\%series\}\_d0) \{\%series\}.correl\\
\indent	freeze(\{\%series\}\_d1) d(\{\%series\},1).correl\\
\indent	freeze(\{\%series\}\_d2) d(\{\%series\},2).correl\\
next\\
group threeserieslogged lindpro lpce lm2real\\
vector(240) ranks\\
for !j = 1 to 240\\
\indent	smpl @first+!j @last-240+!j\\
\indent	var varfirstdifferences.ls 1 4 d(lpce) d(lm2real) d(lindpro)\\
\indent	varfirstdifferences.laglen(12,mname=matrixlags\{!j\})\\
\indent	!lags=matrixlags\{!\j\}(14,5)\\
\indent	freeze(vecmtable!j) threeserieslogged.coint(s,!lags)\\
\indent	ranks(!j)=vecmtable!j(13,4)\\
next\\
freeze(cointegratingranks) ranks.line\\
smpl @all\\
var firstvecm\\
firstvecm.append(coint) b(1,3)=0\\
firstvecm.ec(c,1,restrict) 1 1 lpce lindpro lm2real\\



\end{document}